\documentclass[11pt,letterpaper,sans]{moderncv}
  \usepackage[scale=0.85]{geometry}

  \moderncvstyle{fancy}
  \moderncvcolor{purple}
  \nopagenumbers{}
  \setlength{\hintscolumnwidth}{3.51cm}

  \name{Cristóbal}{Ganter}
  \phone[mobile]{+56~9~7968~7919}
  \email{cganterh@gmail.com}
  \homepage{www.cganterh.net}
  \social[linkedin]{cganterh}
  \social[github]{cganterh}

\begin{document}
  \makecvtitle{}

  \section{Languages}
    \cvitem{Spanish}{First language}
    \cvitem{English}{Advanced}
    \cvitemwithcomment{German}{Intermediate}
      {Sprachdiplom level 2 approved.}

  \section{Education}
    \cventry{2006--2016}{Electronic Engineer}
      {Universidad Técnica Federico Santa María}{Valparaíso}
      {}
      {Majors in Computer Systems and Informatics}

    \cventry{1994--2005}{Pre-University Schooling}
      {Colegio Alemán de Santiago}{Santiago}{}
      {}

  \section{Experience}
    \cventry{2016--present}{Consultant}
      {UTFSM}{Valparaíso}{}
      {
        Consultancy for the project: ``Desarrollo de plataforma Interactiva TIC
        para salas SCALE-UP''.
      }

    \pagebreak[0]

    \cventry{2014--2015}{Freelancer}
      {Reiser Technologies}{Valparaíso}{}
      {
        Front-end development.
      }

    \pagebreak[0]

    \cventry{2014}{MongoDB Consultant}
      {Xompass}{Valparaíso}{}
      {
        Consultancy to optimize the Xompass MongoDB database.
      }

    \pagebreak[0]

    \cventry{2013}{Computing Specialist}
      {SURHGE FIC Project}{Valparaíso}{}
      {
        Activities:
        \begin{itemize}
          \item Linux system administration.
          \item Data analysis.
          \item Web application programming.
          \item Mathematical models programming.
          \item Machine learning.
        \end{itemize}
      }

    \pagebreak[0]

    \cventry{2011--2012}{Teaching Assistant}
      {UTFSM}{Valparaíso}{}
      {
        \emph{Estructura de Datos y Algoritmos}.\newline{}
        Activities:
        \begin{itemize}
          \item Teaching complementary classes.
          % \item Marking of tests and homework.            %delete
          \item Development of a C programming workshop.
          % \item Preparation of test questions.            %delete
        \end{itemize}
      }

    \pagebreak[0]

    \cventry{2010--2011}{Research Assistant}
      {UTFSM}{Valparaíso}{}
      {
      Activities:
        \begin{itemize}
          \item Linux system administration.
          \item Software development related to probabilities using Delphi.
          \item Starting and maintenance of a version control system.
        \end{itemize}
      }

    \pagebreak[0]

    \cventry{2009}{Intern}
      {Wetland}{Santiago}{}
      {
        PLC programming for use in water treatment plants.
      }

    \pagebreak[0]

    \cventry{2005}{Employee}
      {CONAC}{Talca}{}
      {
        Design of a tank level controller.
      }
    %
    % \pagebreak[0]
    %
    % \cventry{2002}{Cleaner}
    %   {Camping Radal}{Reserva Nacional Radal Siete Tazas}{}
    %   {}

  \pagebreak[0]

  \section{Computer Knowledge}
    \subsection{Operating systems}
      \begin{cvcolumns}
        \cvcolumn{Advanced}{Linux}
        \cvcolumn{Intermediate}{Windows}
        \cvcolumn{Beginner}{BSD}
      \end{cvcolumns}

    \pagebreak[0]

    \subsection{Programming languages}
      \begin{cvcolumns}
        \cvcolumn{Advanced}{
          Python\newline{}
          C\newline{}
          CoffeeScript\newline{}
          JavaScript
        }
        \cvcolumn{Intermediate}{
          AWK\newline{}
          Java\newline{}
          Delphi\newline{}
          Pascal
        }
        \cvcolumn{Beginner}{
          PHP\newline{}
          Bash\newline{}
          MATLAB\newline{}
          MIPS\newline{}
          Visual Basic\newline{}
          C++\newline{}
          Ladder
        }
      \end{cvcolumns}

    \pagebreak[0]

    \subsection{Other languages}
      \begin{cvcolumns}
        \cvcolumn{Advanced}{
          HTML5\newline{}
          Markdown\newline{}
          JSON\newline{}
          CSS\newline{}
          SCSS\newline{}
          Makefile
        }
        \cvcolumn{Intermediate}{
          YAML\newline{}
          SVG\newline{}
          XML\newline{}
          Verilog
        }
        \cvcolumn{Beginner}{
          SQL
        }
      \end{cvcolumns}

    \pagebreak[0]

    \subsection{Frameworks}
      \begin{cvcolumns}
        \cvcolumn{Advanced}{
          Tornado Web
        }
        \cvcolumn{Beginner}{
          Flask\newline{}
          Django\newline{}
          Ruby on Rails
        }
      \end{cvcolumns}

    \pagebreak[0]

    \subsection{Tools}
      \begin{cvcolumns}
        \cvcolumn{Advanced}{
          GIT\newline{}
          Inkscape\newline{}
          LibreOffice\newline{}
          Microsoft Office\newline{}
          GNUCash
        }
        \cvcolumn{Intermediate}{
          GIMP
        }
      \end{cvcolumns}

  \pagebreak[0]

  \section{Interests}
    \cvlistitem{Programming}
    \cvlistitem{Science}
    \cvlistitem{Cooking}
    \cvlistitem{Astronomy}

\end{document}
